---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CyTOFprocess

<!-- badges: start -->
<!-- badges: end -->

The goal of CyTOFprocess is to process mass cytometry data in raw fcs format. Currently we have `QC_summary` function that takes in a folder name and then process all the fcs files in the folder to generate a cell count summary for each patient.

## Installation

First install using `install_github` from `devtools` package, then try the script below.

```{r, message=FALSE}
library(CyTOFprocess)
```

## Example

I have prepared a small example using three mock fcs files. Use the following code to see the result

```{r example, message = FALSE}
library(CyTOFprocess)
# generate the summary
knitr::kable(QC_summary(folder = system.file("extdata", package = "CyTOFprocess")))
# remove the output files
unlink(system.file("extdata", "combined.fcs", package = "CyTOFprocess"))
unlink(system.file("extdata", "combined_index.txt", package = "CyTOFprocess"))
```


The package is still under development by Mukai Wang.
